Temporal and Spatial Analysis of Hate Crimes in Toronto

### 2024-09-26 paper/paper.qmd
fixed my dataset

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

# Group by NEIGHBOURHOOD_158 and count the number of hate crimes for each neighborhood
neighborhood_crime_count <- analysis_data %>%
  group_by(NEIGHBOURHOOD_158) %>%
  summarise(Crime_Count = n()) %>%
  arrange(desc(Crime_Count))

# Display the resulting table
print(neighborhood_crime_count)
```

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

@@

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

>>>>

```{r}
#| label: fig-1
#| fig-cap: Sample data visualization of what the data looks like containing the variable of intersts.
#| echo: false
#| warning: false
#| message: false

# Select the variables: Occurrence Date, Bias Types, Neighborhood, Offense, and Arrest
selected_variables <- analysis_data %>%
  select(OCCURRENCE_DATE, RACE_BIAS, RELIGION_BIAS, SEXUAL_ORIENTATION_BIAS, 
         NEIGHBOURHOOD_158, PRIMARY_OFFENCE, ARREST_MADE)

# Display a sample of 10 rows from the selected variables
sample_data <- selected_variables %>%
  sample_n(10)

# Show the table in a nice format using kable
kable(sample_data, caption = "Sample of Cleaned Data with Selected Variables", align = "c")
```

@@

@@

```

A sample observation is shown in @fig-planes. This table indicates neighborhoods in Toronto with more than 20 Hate Crimes from 2018 to 2023. The number of 20 hate crimes is manually selected by the author after inspecting the data to avoid cluster of data. Only the significant neighbourhoods are selected to include in this table to give a brief observation of the hate crime case numbers in different area in Toronto. 
```{r}
#| label: fig-2
#| fig-cap: Neighborhoods with more than 20 Hate Crimes from 2018 to 2023
#| echo: false
#| warning: false
#| message: false

# Filter for neighborhoods with more than 20 hate crimes
neighborhood_filtered <- analysis_data %>%
  group_by(NEIGHBOURHOOD_158) %>%
  summarise(Crime_Count = n()) %>%
  filter(Crime_Count > 20) %>%
  arrange(desc(Crime_Count))

# Display the table using kable.
kable(neighborhood_filtered)
```
